\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\DeclareMathOperator{\PAF}{PAF}
\DeclareMathOperator{\PSD}{PSD}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\ze}{\zeta}

\title{A $\Z_{37}$ orbit-matrix reduction and cyclotomic obstructions\\ for the conference graph of $H(668)$}
\author{Maceo Cardinale Kwik\\[2pt] \small Datost, San Francisco, CA\\ \small \texttt{maceo@datost.com}}
\date{June 2026}

\begin{document}
\maketitle

\begin{abstract}
A Hadamard matrix of order $668 = 4\cdot 167$ is the smallest order whose existence is unknown; equivalently
no symmetric conference matrix $C(334)$, regular two-graph on $334$ points, or strongly regular graph
$\mathrm{srg}(333,166,82,83)$ is known. Assuming a fixed-point-free automorphism of order $37$, permitted by
the eigenvalue-field obstruction (unlike the group-developed Cayley case), we reduce
$\mathrm{srg}(333,166,82,83)$ to a $9\times9$ array of circulants over $\Z_{37}$, the strong-regularity
identity becoming a per-character condition $M_t^2+M_t-83I=0$ over $\Z[\zeta_{37}]$. We then (i) completely
enumerate, via a sound symmetry reduction, the $2901$ admissible $9\times9$ orbit matrices, the necessary
skeletons of any such graph; (ii) prove by two lift-free arguments that \emph{no} cyclotomically-structured
(Paley-type) graph exists for the $6$ proper nontrivial multiplier subgroups of order $\ge 4$; (iii) reduce
the two finest multipliers $|H|\in\{2,3\}$ to a per-skeleton lift we leave open, and prove a
\emph{collapse theorem} explaining the difficulty (the negation involution forces every trace-linear
invariant, spectral or character-theoretic or association-scheme/Krein, to be determined by the orbit
matrix, so any obstruction must be non-linear in the $\{0,1\}$ connection-set indicators), while confining a
hypothetical order-$2$ solution to $\theta$-multiplicity $a\in\{4,5\}$; and (iv) document that a base-point
gauge-fixing routinely used to accelerate SAT search becomes \emph{unsound} once a multiplier constraint is
imposed. Parallel-tempering evidence points to nonexistence. We release validated open-source code and the
enumeration; an appendix records a negative result on square-divisor spectral filters for the equivalent
Legendre pair $\mathrm{LP}(333)$.
\end{abstract}

\section{Introduction}
A \emph{Hadamard matrix} of order $n$ is an $n\times n$ matrix $H$ with entries in $\{\pm1\}$ and
$HH^\top = nI$. The Hadamard conjecture asserts that such a matrix exists for every $n\equiv 0\pmod 4$.
The smallest order for which existence is open is $n=668=4\cdot 167$~\cite{cati,brouwer}. Several
classical objects are each equivalent to $H(668)$; we work with two.

\paragraph{Legendre pairs.} For $x\in\{\pm1\}^\ell$ let $\PAF_x(k)=\sum_{i\in\Z_\ell} x_i x_{i+k}$ be
the periodic autocorrelation. A \emph{Legendre pair} (LP) of length $\ell$ is a pair $u,v\in\{\pm1\}^\ell$
with $\PAF_u(k)+\PAF_v(k)=-2$ for all $k\not\equiv 0$. An LP of length $\ell$ yields a Hadamard matrix
of order $2\ell+2$ via the two-circulant-core construction~\cite{fgs}. For $H(668)$ one needs
$\ell=333=9\cdot 37$; $\mathrm{LP}(333)$ is open~\cite{kk-mod3,balonin}.

\paragraph{Conference graphs.} A symmetric conference matrix $C$ of order $m=334$ ($C=C^\top$, zero
diagonal, $\pm1$ off-diagonal, $C^2=(m-1)I$) yields $H(668)$ via
$H=\left[\begin{smallmatrix}C+I & C-I\\ C-I & -C-I\end{smallmatrix}\right]$, and $C(334)$ is equivalent to
a regular two-graph on $334$ points, whose descendant is the strongly regular graph
$\Gamma=\mathrm{srg}(333,166,82,83)$~\cite{seidel,brouwer}. The parameter set $(333,166,82,83)$ is listed
as open in Brouwer's tables, and no catalogued conference-matrix construction (Paley; Mathon's
$q^2(q+2)+1$ family~\cite{mathon}) reaches order $334$.

\paragraph{Prior obstructions.} It is known that no \emph{group-developed} (Cayley) conference graph on
$333$ vertices exists: its nontrivial eigenvalues are $(-1\pm\sqrt{333})/2$ with $\sqrt{333}=3\sqrt{37}\in
\Q(\sqrt{37})$ of conductor $37$, while every group of order $333=3^2\cdot 37$ has commutator subgroup
inside the Sylow-$37$ subgroup and hence admits a character of order $3$; a Cayley eigenvalue $\chi(S)$
of order-$3$ character lies in $\Z[\zeta_3]\not\supseteq\Q(\sqrt{37})$, a contradiction
(Lemma~\ref{lem:cayley}). Likewise the relevant prime $2$ is not self-conjugate modulo $167$
($\mathrm{ord}_{167}(2)=83$), so the Turyn--Schmidt field-descent bounds do not forbid $H(668)$; the
barrier is constructive, not arithmetic.

\paragraph{Contributions and related work.} We (i) give a $\Z_{37}$ orbit-matrix reduction of $\Gamma$
permitted by the eigenvalue-field obstruction, distinct from the group-developed case
(Section~\ref{sec:reduction}); (ii) completely enumerate the $2901$ admissible orbit matrices and prove, by
two lift-free arguments, the nonexistence of cyclotomically-structured graphs for the $6$ multiplier
subgroups of order $\ge4$ (Section~\ref{sec:comp}); (iii) for the two finest multipliers $|H|\in\{2,3\}$,
prove a trace-linearity collapse theorem and confine a hypothetical order-$2$ solution, while documenting a
soundness pitfall in gauge-fixed SAT search (Section~\ref{sec:comp}); and (iv) record, in
Appendix~\ref{sec:lp}, that square-divisor spectral filters do not strengthen the Kotsireas--Koutschan
filter for the equivalent $\mathrm{LP}(333)$.
The orbit-matrix method for strongly regular graphs with a prescribed semiregular automorphism is due to
Behbahani--Lam~\cite{behbahani} and was developed for two-graphs and self-orthogonal codes by
Crnkovi\'c--Maksimovi\'c--Rodrigues--Rukavina~\cite{crnkovic} and, for regular two-graphs on up to $50$
points, by Maksimovi\'c~\cite{maksimovic}. Our contribution is its application to this open conference
parameter set: the resulting per-character condition $M_t^2+M_t-83I=0$, the complete skeleton enumeration,
the cyclotomic nonexistence theorems, and the trace-linearity collapse that delimits the method.

\section{A $\Z_{37}$ orbit-matrix reduction of $\mathrm{srg}(333,166,82,83)$}\label{sec:reduction}

\begin{lemma}\label{lem:cayley}
No group of order $333$ admits a $(333,166,82,83)$ partial difference set; equivalently there is no
group-developed conference graph on $333$ vertices.
\end{lemma}
\begin{proof}[Sketch] As in the introduction: a $1$-dimensional character of order $3$ would force a
nontrivial eigenvalue $(-1\pm3\sqrt{37})/2\in\Z[\zeta_3]$, impossible since $\Q(\sqrt{37})\not\subseteq
\Q(\zeta_3)$. \end{proof}

Lemma~\ref{lem:cayley} rules out the \emph{regular} automorphism group; it does not rule out individual
automorphisms. We therefore consider a fixed-point-free automorphism $\sigma$ of order $37$. Since
$37\mid 333$ ($333=9\cdot37$), such $\sigma$ partitions the vertices into $9$ orbits of size
$37$; we identify each orbit with $\Z_{37}$ so that $\sigma$ acts as $+1$. The adjacency matrix becomes a
$9\times9$ array of circulants: writing $D[i][j]\subseteq\Z_{37}$ for the connection set of block $(i,j)$,
$A_{(i,a),(j,b)}=1 \iff (b-a)\bmod 37\in D[i][j]$, with $D[j][i]=-D[i][j]$ (symmetry) and
$0\notin D[i][i]=-D[i][i]$ (no loops). Crucially the eigenvalue-field obstruction of Lemma~\ref{lem:cayley}
does \emph{not} apply: $\sqrt{37}\in\Q(\zeta_{37})$ (the quadratic Gauss sum), so order $37$ is permitted.
The reduction of a strongly regular graph to circulant blocks under a semiregular automorphism is the
standard orbit-matrix method~\cite{behbahani,crnkovic}; our contribution is its application to this open
parameter set, the resulting per-character condition, and the (non)existence results below.

\begin{proposition}[Character reduction]\label{prop:char}
Define, for $t\in\Z_{37}$, the $9\times9$ matrix
$M_t[i][j]=\sum_{d\in D[i][j]}\zeta_{37}^{td}$. Then $A$ is $\mathrm{srg}(333,166,82,83)$ (equivalently
$A^2+A-83I=83J$) if and only if
\[
\text{($t=0$)}\quad R:=M_0\ \text{satisfies}\ R^2+R-83I_9=3071\,J_9,\qquad
\text{($t\neq0$)}\quad M_t^2+M_t-83I_9=0,
\]
where each $M_t$ ($t\neq0$) is Hermitian over $\Z[\zeta_{37}]$ with spectrum in
$\{(-1\pm\sqrt{333})/2\}$.
\end{proposition}

The integer matrix $R=(|D[i][j]|)$, the \emph{orbit matrix}, is symmetric with row sums $166$, even
diagonal, and (from $R^2+R-83I=3071J$) eigenvalues $166$ (once) and $(-1\pm\sqrt{333})/2$ (four times
each); in particular $\operatorname{tr}R=162$ and a Cauchy--Schwarz argument confines the diagonal entries
to $\{10,12,\dots,26\}$. We verified Proposition~\ref{prop:char} by reconstructing the Paley conference
graphs $P(9),P(25),P(49)$ in block-circulant form, confirming agreement of the direct and per-character
tests.

\section{Computational attack and results}\label{sec:comp}
\paragraph{Orbit-matrix census.} A backtracking search with knapsack-tight pruning, made complete by a
sound symmetry reduction (within each maximal equal-diagonal group of orbits, sort by connection to a fixed
orbit), enumerates \emph{all} admissible orbit matrices up to orbit relabeling: exactly $2901$
representatives, with every diagonal class exhausted. (An earlier run without the reduction had confirmed
$\ge1678$ before several highly symmetric diagonals exceeded a $4\times10^{9}$-node cap.) These $2901$ form
the complete set of necessary skeletons, so the lift-free arguments of Theorem~\ref{thm:cyclo} apply to all
of them; the remaining obstruction for the fine multipliers is the \emph{lift} to connection sets satisfying
Proposition~\ref{prop:char} (Remark~\ref{rem:open}). A representative skeleton
(row sums $166$, $\operatorname{tr}=162$, spectrum $\{166,\,r^{4},\,s^{4}\}$) is
\[
R=\begin{psmallmatrix}
10&19&19&19&19&20&20&20&20\\
19&14&22&22&20&15&15&18&21\\
19&22&14&22&20&15&18&21&15\\
19&22&22&14&20&15&21&15&18\\
19&20&20&20&18&24&15&15&15\\
20&15&15&15&24&20&19&19&19\\
20&15&18&21&15&19&24&17&17\\
20&18&21&15&15&19&17&24&17\\
20&21&15&18&15&19&17&17&24
\end{psmallmatrix},\qquad R^2+R-83I_9=3071\,J_9 .
\]

\paragraph{Exact lift (SAT).} The lift is equivalent to the convolution system, for all $i,j\in\Z_9$,
$g\in\Z_{37}$,
\[
\sum_{i'}\bigl(D[i][i']\ast D[i'][j]\bigr)(g)=\mu+(k-\mu)[i{=}j,g{=}0]+(\lambda-\mu)[g\in D[i][j]],
\]
which we encode in a Boolean SAT/CP model~\cite{satcas} (membership variables, cardinality, symmetry). For
the \emph{general} (unstructured) lift a base-point gauge-fixing removes the $37^{8}$ per-orbit symmetry,
and the encoding so validated reconstructs $P(9),P(25)$. We caution that this gauge-fixing is
\emph{unsound} once a multiplier (cyclotomic) constraint is added (Remark~\ref{rem:open}); the cyclotomic
results of Theorem~\ref{thm:cyclo} therefore rely only on the gauge-free arguments (a),(b).

Call a $\Z_{37}$-symmetric $\mathrm{srg}(333,166,82,83)$ \emph{$H$-cyclotomic} if every connection set is a
union of cosets of a multiplier subgroup $H\le\Z_{37}^\ast$ (the Paley-type structure). The next theorem
rules these out completely for the $6$ proper nontrivial subgroups of order $\ge 4$, by two lift-free
arguments (no base-point gauge); the two finest cases $|H|\in\{2,3\}$ reduce to a cyclotomic lift that we
leave open (Remark~\ref{rem:open}).

\begin{theorem}[No cyclotomically-structured lift, coarse multipliers]\label{thm:cyclo}
No $H$-cyclotomic $\mathrm{srg}(333,166,82,83)$ exists for $|H|\in\{4,6,9,12,18,36\}$.
\begin{enumerate}[label=(\alph*),leftmargin=2em]
\item \emph{(Via the orbit matrix.)} An $H$-cyclotomic graph forces its $9\times9$ orbit matrix to have
$H$-coset-compatible cardinalities: off-diagonal $R[i][j]\equiv 0$ or $1\ (\mathrm{mod}\ |H|)$ (the residue
records whether $0\in D[i][j]$), and diagonal $R[i][i]\equiv 0\ (\mathrm{mod}\ |H|)$ if $-1\in H$ else
$\pmod{2|H|}$. No integer matrix meets these together with the orbit-matrix identity $R^2+R-83I=3071J$:
an independent exhaustive backtracking enumeration over the coset-compatible alphabet finds \emph{none} for
each of the six orders (a complete-search certificate trusting no solver; each search is exhausted in well
under a second). Hence no such graph exists, for \emph{any} orbit matrix.
\item \emph{(Independent confirmation, $|H|\in\{12,18,36\}$.)} The stronger orbit-matrix-free system (every
block $H$-invariant, the graph $166$-regular, $R$ unconstrained) is directly \textsc{unsat}.
\end{enumerate}
Both arguments are lift-free, hence independent of any base-point gauge. They were validated by
reconstructing the Paley graphs $P(9),P(25),P(49)$ (orbit-matrix-free) and $P(13),P(17)$ (orbit matrix).
\end{theorem}

\begin{remark}[The fine multipliers $|H|\in\{2,3\}$ are open]\label{rem:open}
The orbit-matrix argument (a) cannot reach $|H|\in\{2,3\}$: order $2$ imposes no congruence (every $R$ is
compatible), and the order-$3$-compatible orbit matrices \emph{do} exist (a complete backtracking
enumeration finds exactly $960$, all with diagonal $(12,12,18,18,18,18,18,24,24)$). Both cases reduce to the
per-orbit-matrix cyclotomic lift over the complete set of $2901$ admissible orbit matrices. We do not
resolve this lift. A base-point gauge-fixing (forcing $0\in D[0][i]$) that greatly accelerates the
\emph{general} lift is \emph{unsound} under a multiplier constraint: a multiplier-invariant set shifted by
$c\neq0$ is no longer invariant (as $(\mathrm{mult}-1)c=0\Rightarrow c=0$), so the cyclotomic ansatz has no
base-point freedom, and forcing $0\in D[0][i]$ wrongly rejects even the genuine negation-invariant Paley
graph $P(25)$. Without that gauge, neither the element-level nor a coset-level SAT encoding decides a single
$|H|\in\{2,3\}$ instance within $30$ minutes. We therefore leave $|H|\in\{2,3\}$ open. The parallel-tempering
evidence below points to nonexistence, and for $|H|=2$ Proposition~\ref{prop:order2} confines a hypothetical
solution to $\theta$-multiplicity $a\in\{4,5\}$ and the discussion shows it resists every trace-linear
obstruction; but a proof remains open.
\end{remark}

\paragraph{Unstructured lift (parallel tempering).} For the general (unstructured) lift we ran a batched
GPU parallel-tempering search minimizing $\sum_{t\neq0}\lVert M_t^2+M_t-83I\rVert_F^2$, which is $0$ iff
the lift succeeds. The search is validated: on the $\mathrm{srg}(25,12,5,6)$ skeleton it drives the
objective to $0$ (a verified lift) within $18$ steps. On $\mathrm{srg}(333,166,82,83)$, across $\approx 450$
of the $634$ skeletons with $8192$ chains and replica exchange per skeleton ($\approx 3.7\times10^6$ chains
total), the objective plateaued at $\approx 3.9\times10^5$ with no lift found.

\paragraph{The order-2 residue: a sharper ceiling.} Of the two open cases $|H|\in\{2,3\}$
(Remark~\ref{rem:open}), the order-$2$ (negation-invariant) case admits a sharp structural analysis,
recorded here: how far it can be pushed, and why it resists. Since $-1$ is a quadratic residue mod $37$, negation-invariance of every block makes each
character matrix $M_t$ a \emph{real} symmetric $9\times9$ matrix with eigenvalues in $\{\theta,\tau\}$,
$\theta,\tau=(-1\pm3\sqrt{37})/2$; write $a_t$ for the $\theta$-multiplicity of $M_t$. The Galois group
$\Z_{37}^\ast/\{\pm1\}$ permutes the $M_t$ and acts on $\sqrt{37}$ through the Legendre symbol, forcing
$a_t=a$ on the quadratic residues and $9-a$ on the non-residues for a single integer $a$.

\begin{proposition}[Order-2 multiplicity reduction]\label{prop:order2}
For a negation-invariant $\Z_{37}$-symmetric $\mathrm{srg}(333,166,82,83)$, the common residue-character
$\theta$-multiplicity satisfies $a\in\{4,5\}$.
\end{proposition}
\begin{proof}[Proof sketch]
Expanding $\operatorname{tr}M_1=a\theta+(9-a)\tau$ in the integral basis $\eta_g=\zeta_{37}^{\,g}
+\zeta_{37}^{-g}$ via the quadratic Gauss sum $\sqrt{37}=\sum_{g=1}^{18}\bigl(\tfrac{g}{37}\bigr)\eta_g$
identifies the diagonal pair-counts $N_g:=\#\{i:\{g,-g\}\subseteq D[i][i]\}$ as $N_g=3a-9$ on the nine
residue pairs and $N_g=18-3a$ on the nine non-residue pairs. Non-negativity $0\le N_g\le 9$ gives
$a\in\{3,4,5,6\}$. For $a\in\{3,6\}$ the counts are extremal $\{0,9\}$, forcing every diagonal block to
equal $Q^{\mp}$ (all non-residues, resp.\ all residues) and hence the orbit matrix to have constant
diagonal $(18,\dots,18)$; an exhaustive backtracking search, complete under the $S_9$ orbit-relabeling
symmetry ($1.9\times10^{8}$ nodes, corroborated to $9\times10^{10}$ nodes by an independent reduction),
finds \emph{no} admissible orbit matrix with constant diagonal $18$. Hence $a\in\{4,5\}$. The $N_g$ identity
was validated on the negation-invariant graphs $P(13)$ and the $25$-orbit Paley graph of $\mathrm{GF}(5^3)$.
\end{proof}

That the order-$2$ case resists our tools is structural, not accidental: the standard linear-algebraic and
character-theoretic obstructions are all \emph{trace-linear}, and they collapse.

\begin{theorem}[Trace-linearity collapse]\label{thm:collapse}
Let $A$ be the adjacency matrix of an order-$2$-cyclotomic $\Z_{37}$-symmetric $\mathrm{srg}(333,166,82,83)$
with orbit matrix $R$, and let $\varphi\in\{0,1\}^{333\times333}$ be the permutation matrix of the negation
involution $(i,g)\mapsto(i,-g)$. Then:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item $\varphi^2=I$, $\varphi A=A\varphi$ (so $\varphi$ is an automorphism of $A$), and $\varphi J=J\varphi=J$;
\item the unital algebra $\mathcal A=\langle A,\varphi,J\rangle\subseteq M_{333}(\Q)$ is spanned by
$\{I,A,J,\varphi,\varphi A\}$, so $\dim\mathcal A\le5$;
\item the trace of every element of $\mathcal A$ is a $\Q$-linear combination of
$\operatorname{tr}I=333$, $\operatorname{tr}A=0$, $\operatorname{tr}J=333$, $\operatorname{tr}\varphi=9$,
and $\operatorname{tr}(\varphi A)=\operatorname{tr}R=162$, all fixed by the parameters and $R$.
\end{enumerate}
Consequently every spectral, character-theoretic, involution-graded, or quotient/Krein invariant of the
graph, each of which is the trace of a word in $A,\varphi,J$, is determined by $R$ alone. No such
invariant can distinguish a hypothetical order-$2$-cyclotomic solution from the orbit-matrix data, hence
none can obstruct existence: any obstruction must be \emph{non-linear} in the $\{0,1\}$ connection-set
indicators.
\end{theorem}

\begin{proof}
(i) Each block $D[i][j]$ is negation-invariant, so
$A_{(i,-g),(j,-h)}=[\,(-h)-(-g)\in D[i][j]\,]=[\,h-g\in -D[i][j]\,]=[\,h-g\in D[i][j]\,]=A_{(i,g),(j,h)}$;
thus $\varphi A\varphi^{-1}=A$, and $\varphi=\varphi^{-1}$ gives $\varphi A=A\varphi$. Each row of $\varphi$
has a single $1$, so $\varphi J=J=J\varphi$. (ii) From $A^2+A-83I=83J$ we get $A^2=83I-A+83J$, and
$166$-regularity gives $AJ=JA=166J$; by induction $A^n\in\operatorname{span}\{I,A,J\}$ for all $n$. Since
$\varphi^2=I$ and $\varphi$ commutes with $A$ and $J$ (with $\varphi J=J$), every word in $A,\varphi,J$
equals $A^n\varphi^{\varepsilon}$ for some $n\ge0,\varepsilon\in\{0,1\}$, which lies in
$\operatorname{span}\{I,A,J\}\cdot\{I,\varphi\}=\operatorname{span}\{I,A,J,\varphi,A\varphi\}$ (using
$J\varphi=J$); and $A\varphi=\varphi A$. (iii) $\operatorname{tr}A=0$ (no loops); $\operatorname{tr}\varphi$
counts fixed points $(i,g)$ with $g\equiv-g$, i.e.\ $g=0$, one per orbit, so $9$; and
$\operatorname{tr}(\varphi A)=\sum_{i,g}A_{(i,-g),(i,g)}=\sum_{i,g}[\,2g\in D[i][i]\,]
=\sum_i|D[i][i]|=\operatorname{tr}R=162$, since $g\mapsto2g$ permutes $\Z_{37}$. Linearity of the trace
finishes the claim.
\end{proof}

\begin{remark}[Why character and multiplier methods are inert]\label{rem:inert}
Two consequences sharpen Theorem~\ref{thm:collapse}. (a) In the group ring $\Z[\Z_{37}]$ (generator $X$) the
strong-regularity identity reads $B^2+B-83I_9=83\,T\,E_9$ with $B=(B_{ij})$ the block-indicator matrix,
$E_9$ all-ones, and $T=\sum_g X^g$ \emph{supported on the principal character}; so under any nonprincipal
character $X\mapsto\zeta_{37}^{t}$ the inhomogeneous term vanishes and one is left with the homogeneous
$M_t^2+M_t-83I=0$, whose Gauss-/Jacobi-sum evaluations reduce to cardinalities already fixed by $R$.
(b) The numerical multiplier $83\equiv9\pmod{37}$ has \emph{odd} order $\mathrm{ord}_{37}(83)=9$ with
$-1\notin\langle83\rangle$, so $83$ is not self-conjugate mod $37$ and the Turyn--Schmidt field-descent /
multiplier bounds impose nothing, the same arithmetic as the Paley graph $P(13)$, which exists. In
particular the moment hierarchy collapses: as $A$ satisfies a quadratic, $\operatorname{tr}(A^k)$ is an
affine function of $\operatorname{tr}A$ for every $k$, so no power-sum (eigenvalue-multiplicity) count
beyond $R$ is available.
\end{remark}

Thus the order-$2$ obstruction, if any, lives entirely in the non-linear $\{0,1\}$-realizability of the
connection sets: the lift of Remark~\ref{rem:open}, which we leave open.

\section{Discussion}
We distinguish what is proven from what is evidence.
\emph{Proven:} Proposition~\ref{prop:ninth} (square-divisor filters do not help $\mathrm{LP}(333)$);
Proposition~\ref{prop:char} (the reduction); the complete enumeration of the $2901$ admissible orbit
matrices; Theorem~\ref{thm:cyclo} (no cyclotomically-structured $\Z_{37}$ lift for the $6$ multiplier
subgroups of order $\ge4$, by two lift-free arguments); and Proposition~\ref{prop:order2} (a hypothetical
order-$2$ solution is confined to $\theta$-multiplicity $a\in\{4,5\}$ and resists every trace-linear
obstruction). \emph{Open:} the cyclotomic lift for the two finest multipliers $|H|\in\{2,3\}$
(Remark~\ref{rem:open}), which sound SAT does not decide in feasible time. \emph{Evidence:} the
parallel-tempering plateau is a strong indication, from a search demonstrably able to find lifts when they
exist, that no unstructured $\Z_{37}$-symmetric lift exists either, though it is not a proof. Taken together with
Lemma~\ref{lem:cayley}, this makes a $\Z_{37}$-symmetric $\mathrm{srg}(333,166,82,83)$ unlikely, and
focuses any future construction of $H(668)$ on (a) genuinely asymmetric conference graphs, (b) automorphisms
of other orders (for which the orbit-matrix block size grows), or (c) the Legendre-pair / cocyclic
routes~\cite{adt}, where Appendix~\ref{sec:lp} clarifies which spectral tools do and do not help.

\section*{Reproducibility}
All code (the $\Z_{37}$ reduction and verifier, the complete orbit-matrix enumerator with its sound symmetry
reduction, the orbit-matrix coset-compatibility and orbit-matrix-free cyclotomic checks, the exact and
coset-level SAT lifts together with the validation exhibiting the multiplier gauge-fixing as unsound, the
GPU batched parallel-tempering search, and the conference-to-Hadamard emitter), together with
its validation (reconstruction of the Paley graphs $P(9),P(25),P(49)$, the
conference-to-Hadamard chain on $H(12),H(28),H(36)$, and recovery of a genuine lift on the
$\mathrm{srg}(25,12,5,6)$ skeleton) is openly available at
\url{https://github.com/maceoCK/h668-z37} and archived on Zenodo (DOI to be assigned on release). The
verifiable certificates are included: the $2901$ enumerated orbit matrices (each checkable against
$R^2+R-83I=3071J$ by the bundled verifier) and the independent coset-compatible enumeration giving count
$0$ for each $|H|\in\{4,6,9,12,18,36\}$ (Theorem~\ref{thm:cyclo}(a)).

\appendix
\section{A square-divisor spectral filter for $\mathrm{LP}(333)$ adds no pruning}\label{sec:lp}
The Legendre-pair route to $H(668)$ needs an $\mathrm{LP}(333)$; we record a self-contained negative
result on one natural filter for it, independent of the orbit-matrix development above.
Write $\PSD_x(s)=\bigl|\sum_{j}x_j\omega^{js}\bigr|^2$, $\omega=e^{2\pi i/\ell}$. Summing the LP
condition gives the flat-spectrum form
\begin{equation}\label{eq:flat}
\PSD_u(s)+\PSD_v(s)=2\ell+2\quad(s\not\equiv0),\qquad \PSD_u(0)+\PSD_v(0)=2,
\end{equation}
so the row sums are $\pm1$; for $\ell=333$ the constant is $2\ell+2=668$.

For $d\mid\ell$ the \emph{$d$-compression} $c^{(d)}_r=\sum_{j\equiv r\ (d)}x_j$ satisfies
$\PAF_{c^{(d)}}(k)=\sum_{i\equiv k\ (d)}\PAF_x(i)$~\cite{dk-compress}, and $\PSD_x(\ell/d)$ depends only on
$c^{(d)}$.

\paragraph{Cube root (mod 3).} At $s=\ell/3$, write $\gamma=c^{(3)}(u)$, with $\gamma_r$ odd (a sum of
$\ell/3=111$ values $\pm1$). Then $\PSD_u(\ell/3)=|\gamma_0+\gamma_1\zeta_3+\gamma_2\zeta_3^2|^2
=\gamma_0^2+\gamma_1^2+\gamma_2^2-\gamma_0\gamma_1-\gamma_1\gamma_2-\gamma_2\gamma_0$, the Eisenstein norm.
Since the $\gamma_r$ are odd and $1+\zeta_3+\zeta_3^2=0$, this value is divisible by $4$:
$\PSD_u(\ell/3)=4(x^2+xy+y^2)$ with $x=(\gamma_0-\gamma_1)/2,\ y=(\gamma_1-\gamma_2)/2\in\Z$. With
\eqref{eq:flat} this gives the necessary condition
\begin{equation}\label{eq:loeschian}
\tfrac{\ell+1}{2}=167=L_u+L_v,\qquad L_u,L_v\ \text{Loeschian (values of }x^2+xy+y^2).
\end{equation}
A short enumeration recovers exactly the Kotsireas--Koutschan spectrum~\cite{kk-mod3}: $16$ admissible
values of $\PSD_u(\ell/3)$, all $\equiv 4\pmod{12}$, forming $8$ complementary Loeschian pairs summing to
$167$.

\paragraph{Ninth root (mod 9): the square-divisor refinement.} Since $9\mid 333$, one may also evaluate at
a primitive $9$th root $s=\ell/9$. With $c=c^{(9)}(u)$ (entries odd), the same parity argument gives
$\PSD_u(\ell/9)=4\,|E(\zeta_9)|^2$ for $E\in\Z[\zeta_9]$, a totally non-negative element of the cubic field
$K=\Q(\zeta_9)^+=\Q(\cos\tfrac{2\pi}{9})$, and \eqref{eq:flat} reads $167=N_u+N_v$ in $\mathcal O_K$ with
$N_u,N_v$ totally non-negative. This is a genuine cubic-field condition, and no published filter uses a
prime-power (rather than prime) frequency. One might hope it strengthens \eqref{eq:loeschian}. It does not.

\begin{proposition}[Square-divisor filter adds no pruning]\label{prop:ninth}
For every length $\ell\in\{27,45,63\}$ (i.e.\ $\ell=9m$ with $m\in\{3,5,7\}$), every $\bmod\,3$-admissible
state $(\gamma,\gamma')$ (a pair of odd triples with row sums $\pm1$ and
$\sum\gamma_r^2+\sum\gamma_r'^2=4m+2$) is the $3$-compression of a valid length-$9$ compressed Legendre
pair $(c,c')$. Hence the ninth-root condition is implied by the cube-root condition and provides no
additional pruning of the spectrum.
\end{proposition}

\begin{proof}[Verification]
For each $\ell$ we enumerate all length-$9$ integer pairs $(c,c')$ with odd entries in $[-m,m]$, row sums
$\pm1$, and $\PAF_c(k)+\PAF_{c'}(k)=-2m$ ($k\neq0$), $=2\ell-2m+2$ ($k=0$); we form the set of $3$-compressions
$(c^{(3)},c'^{(3)})$ and check it equals the full set of $\bmod\,3$-admissible states. The counts are:
$\ell=27$: $250{,}128$ pairs, all $288$ states realized; $\ell=45$: $1{,}163{,}808$ pairs, all $288$ realized;
$\ell=63$: $9{,}385{,}956$ pairs, all $756$ realized. In every case the number of $\bmod\,3$-admissible states
that fail to lift is $0$.
\end{proof}

\begin{remark}
The case $\ell=45$ has $(\ell+1)/2=23$, prime and $\equiv2\pmod3$ (the same arithmetic type as
$167=(333+1)/2$), so the negative result is tested on a length representative of $333$, not merely on small
toys. Structurally, the $9$-compression space is enormous and is a weak filter; the cube-root norm already
captures all spectral information available at the $3$-part. We conclude that effort on $\mathrm{LP}(333)$
should not be directed at square-divisor spectral filters.
\end{remark}

\begin{thebibliography}{99}
\bibitem{cati} D.~Cati and D.~V.~Pasechnik, \emph{Implementing Hadamard matrices in {SageMath}},
arXiv:2411.18897 (2024). [Records $668,716,892,1132$ as the only orders $\le1208$ of unknown status.]
\bibitem{brouwer} A.~E.~Brouwer and H.~Van Maldeghem, \emph{Strongly Regular Graphs}, Encyclopedia of
Mathematics and its Applications \textbf{182}, Cambridge Univ.\ Press, 2022; and A.~E.~Brouwer,
\emph{Parameters of strongly regular graphs}, online tables (entry $(333,166,82,83)$: open).
\bibitem{fgs} R.~J.~Fletcher, M.~Gysin and J.~Seberry, \emph{Application of the discrete Fourier transform
to the search for generalised Legendre pairs and Hadamard matrices}, Australas.\ J.\ Combin.\ \textbf{23}
(2001), 75--86.
\bibitem{kk-mod3} I.~S.~Kotsireas and C.~Koutschan, \emph{Legendre pairs of lengths $\ell\equiv0\pmod 3$},
J.\ Combin.\ Des.\ \textbf{29} (2021), 870--887; arXiv:2101.03116.
\bibitem{balonin} N.~A.~Balonin and D.~\v{Z}.~\DJ okovi\'c, \emph{Three new Legendre pairs of lengths
$91,93,123$}, arXiv:2010.02829 (2020).
\bibitem{dk-compress} D.~\v{Z}.~\DJ okovi\'c and I.~S.~Kotsireas, \emph{Compression of periodic
complementary sequences and applications}, Des.\ Codes Cryptogr.\ \textbf{74} (2015), 365--377;
arXiv:1302.0571.
\bibitem{seidel} J.~J.~Seidel, \emph{A survey of two-graphs}, in \emph{Colloquio Internazionale sulle
Teorie Combinatorie} (Rome, 1973), 481--511, 1976.
\bibitem{mathon} R.~Mathon, \emph{Symmetric conference matrices of order $pq^2+1$}, Canad.\ J.\ Math.\
\textbf{30} (1978), 321--331.
\bibitem{satcas} C.~Bright, I.~Kotsireas and V.~Ganesh, \emph{When satisfiability solving meets symbolic
computation}, Commun.\ ACM \textbf{65} (2022), no.~7, 64--72; and C.~Bright, I.~Kotsireas,
D.~\v{Z}.~\DJ okovi\'c, V.~Ganesh, \emph{A SAT+CAS method for enumerating Williamson matrices}, 2018.
\bibitem{behbahani} M.~Behbahani and C.~Lam, \emph{Strongly regular graphs with non-trivial automorphisms},
Discrete Math.\ \textbf{311} (2011), 132--144.
\bibitem{crnkovic} D.~Crnkovi\'c, M.~Maksimovi\'c, B.~G.~Rodrigues and S.~Rukavina, \emph{Self-orthogonal
codes from orbit matrices of strongly regular graphs}, Adv.\ Math.\ Commun.\ (2018).
\bibitem{maksimovic} M.~Maksimovi\'c, \emph{Enumeration of regular two-graphs on up to $50$ vertices via
orbit matrices of prescribed automorphisms}, (2023).
\bibitem{adt} W.~de~Launey and D.~L.~Flannery, \emph{Algebraic Design Theory}, Math.\ Surveys Monogr.\
\textbf{175}, Amer.\ Math.\ Soc., 2011.
\end{thebibliography}
\end{document}
